\section{Tareas 2} 

\begin{enumerate}[1.]
	\item Why is it more efficient to combine SQL statements into PL/SQL blocks?
	\\
	\\it is more efficient to use SQL statements within PL/SQL blocks because network traffic can be decreased significantly, and application becomes more efficient as well.
	\\ go
	\\ 
	\item Why is it beneficial to use PL/SQL with an Oracle database? List at least three reasons. 
	\\
	\\1) It allows the programmer to combine procedural constructs with SQL.
\\2) The basic unit of a PL/SQL program is a block, and blocks allow the
programmer to create code that is easier to read and maintain.
\\3) PL/SQL allows the programmer to combine multiple SQL statements into a
single PL/SQL program. Sending a single PL/SQL program to the database
server for processing is more efficient than sending multiple SQL statements.
\\4) PL/SQL is integrated into several Oracle tools such as Forms, Reports, and
Oracle Application Express.
\\5) You can develop PL/SQL code on one operating system and deploy it on another
operating system because PL/SQL code is independent of the operating system
and the platform.
\\6) PL/SQL allows the programmer to prepare for errors by writing exception
handling logic into code; PL/SQL easily handles data-oriented exceptions such
as no data found and too many rows. 
	\\

	\item How is PL/SQL different from C and Java? List three differences. 
\\
\\1) PL/SQL requires a database or Oracle tool..
\\2) PL/SQL allows for some object-oriented programming techniques, but is not as
extensive as Java.
\\3) PL/SQL is the most efficient language to use with an Oracle database.
\\4) PL/SQL is portable to other operating systems, as long as it is running a
compatible Oracle database (that is, a database with the same version).
\\5) PL/SQL is easier to learn than C and Java. 
\\
	\item List three examples of what you can build with PL/SQL code. 
\\
\\Using PL/SQL, you can:
\\1) Create Web and other applications
\\2) Manage application data (write programs for DDL or DML)
\\3) Manage the Oracle database (write programs for security, for managing
database jobs)
\\4) Create custom reports
	

\end{enumerate} 
